Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-16 vesicle_code/docs/permeableVes/main.tex
yny

%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
%Physics}
\title{Hydrodynamics of a Semi-Permeable Vesicle Under Flow and
Confinement???}

@@

%
%\paragraph{Literature to maybe cite}
%\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
%happens in regions where proteins congregate and this can lead to
%semi-permeability?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Formulation}
We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:schematics}.
To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$).
On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
and the membrane velocity $\dot{\bf x}$ \cite{yao-mor2017}:
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
is the arclength along the membrane, see figure~\ref{fig:schematics}. Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 1$ mol/L, the permeable water flow is of the order $v_\mathrm{o}=1 \mu$m/s. Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution 
($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-3}:10^{-7}$. We note that this result shows that the osmotic stress contributes much more to the permeable water flow than then tension and bending stresses. Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
In the following we will explore both.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Effects of membrane water permeability}
We consider a single semi-permeable vesicle in familiar configurations to highlight the effects of membrane water permeability.
In free space we put a semi-permeable vesicle in a quiescent flow, a planar shear flow and a Poiseuille flow.
We also consider a semi-permeable vesicle in confinement: a long channel and a contracting channel.
For each example, we fix the vesicle length and examine the enclosed area as a dynamical consequence of water flow, vesicle shape deformation and membrane tension distribution.
%
%all vesicles have a length
%$L$, but the area is not conserved because of semi-permeability. We vary
%the initial vesicle reduced area, the permeability rate, and the flow
%rate. For all simulations, the bending modulus is $10^{-19}J$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}
Our analysis shows that a semi-permeable vesicle in a quiescent flow
relaxes to a circle at a rate that is proportional to $\beta$, and the
steady state tension is $\Lambda = 2\pi^2/L^2$. Therefore, the times for
the vesicle to deviate from its initial reduced area and to reach its
steady state are proportional to $\beta^{-1}$. This is verified for a
vesicle with initial reduced area $\alpha = 0.65$ and with different
semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
to be within 1.3\% of its steady state reduced area, and the required
time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
1.3\% of its initial reduced area. Both times are proportional to
$\beta^{-1}$, and for this reason, our numerical results are reported in
terms of the scaled time $\beta t$.
\begin{table}[htp]
  \centering
  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
  inflating ($t_\mathrm{inflate}$).}
  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
    $\beta$ & $t_\mathrm{steady}$  & ratio 
            & $t_\mathrm{inflate}$ & ratio \\
    \midrule
    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
              & $2.17 \times 10^{-2}$ & --- \\ 
    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
                $1.25 \times 10^{-1}$ & 5.76 \\
    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
                $1.59 \times 10^{0}$ & 12.72 \\
    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
                $2.19 \times 10^{1}$ & 13.77 \\
    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
                $2.14 \times 10^{2}$ & 9.77 \\
    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
                $2.20 \times 10^{3}$ & 10.14 \\
    \bottomrule
  \end{tabular}
\end{table}

In Figure~\ref{fig:relaxationComposite}, we examine the transient
dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
initial configurations. As expected, each vesicle eventually
reaches a circular shape with reduced area $\alpha=1$. Next, we observe
that even though the vesicle is inflating to a circle, meaning that
there is a net flux into the vesicle, there are regions where the flux
is out of the vesicle. These regions are denoted in blue and are only
present at early times. Finally, the vesicles's reduced area do not 
change by much at early times, and intermediate shapes of semi-permeable vesicles
resemble the shape of an impermeable vesicle. This can be explained by
considering the two terms that contribute to the vesicle velocity: (i)
the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the
force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the
permeability velocity is much smaller than the force balance velocity at
early times, and the semi-permeable vesicle dynamics resembles those of
an impermeable vesicle. As the force balance velocity decreases, the
permeability velocity dominates, and the vesicle begins to inflate to a
circle with no vanishing force and velocity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a).}
\end{figure}

We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. A vesicle's reduced area
and viscosity contrast determine whether it tank treads or
tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Similar to the
dynamics of an impermeable vesicle, a semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics. Since we
consider semi-permeable vesicles, there is no viscosity contrast and
we do not observe tumbling.

@@

We form the steady state shape for a variety of semi-permeability rates
and flow rates. Since the final shape is independent of the initial
reduce area, for all simulations we initialize the vesicle with reduced
area $\alpha = 0.65$. The steady state vesicle shape and its reduced
area are in Figure~\ref{fig:shearComposite}(b). We see that the flow
rate significantly affects the final vesicle shape, but the
semi-permeability rate has a minor effect. Instead, as we saw in the
quiescent analysis, $\beta$ sets a time scale since the time required
for a vesicle to reach its steady state configuration is proportional to
$\beta^{-1}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure*}[htp]
  \ifTikz
  \centering
  \input{figures/parabolicComposite.tikz}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
  a semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The fluid flux along the red
  regions is into the vesicle, and the fluid flux along the blue regions
  is out of the vesicle.  (b) The steady state inclination angle for
  four different flow velocities. The steady state shapes are
  superimposed. (c) The reduced area of the slipper formed with the flow
  rate of 800 $\mu m/s$. (d) The vesicle shape shown with the background
  imposed flow. The channel width is 12.5 times larger than the vesicle
  radius. The corresponding reduced area of each vesicle is indicated by
  the marks in plot (c).}
\end{figure*}

We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
the effect of the non-linear Poiseuille flow on the migration of
semi-permeable vesicle. In this experiment, the vesicle is initialized
above the center line $y=0$, and it migrates towards the center
line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
the vesicles reduced area and the flow rate, the long time vesicle shape
is either an axisymmetric parachute or bullet, or an asymmetric
tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
for the steady state shape of an impermeable vesicle
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

Having validated our method, we investigate the dynamics of a
semi-permeable vesicle in a Poiseuille flow. Using several initial
reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
final vesicle configurations are in
Figure~\ref{fig:parabolicComposite}(b). As observed for the shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the steady state reduced area in
Figure~\ref{fig:parabolicComposite}(b). At the smallest flow rate of $U
= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
We consider the effect of stenosis on a semi-permeable vesicle. Inspired
by an experiment that measures the effects of cells on the dynamical
pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we first examining the effect of
semi-permeability on the pressure fluctuation across a stenosed
geometry. In this experiment, a pressure drop is used to pass a vesicle
red blood cell (RBC) through a constriction with diameter $5\mu$m and
length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow rate is chosen so that
the residency time of the RBC in the constriction agrees with the
experimental results. When the RBC enters the constriction, the result
is an increase in the pressure drop required to maintain a constant flow
rate, and the difference between these pressures is called the excess
pressure. We consider both an impermeable and semi-permeable vesicle
with initial reduced area $\alpha = 0.65$ passing through a constricted
geometry and compute the pressure drop between the inlet and outlet of
the constriction. In Figure~\ref{fig:stenosisComposite}(c), we plot the
excess pressures. The impermeable case agrees with experimental
results~\cite{abk-fai-sto2006} (see Figure 3), and the results indicate
that less pressure is required to maintain a constant flow rate when the
vesicle is semi-permeable. Our simulations indicate the
semi-permeability does affect the excess pressure, and the vesicle's
reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a much longer constriction, and we observe that the reduced area
decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).

@@

@@

Velocity scale is $100\mu$m/s.

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
  the vesicle height is initially $10\mu$m, and the maximum background
  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
  into the vesicle, and the fluid flux along the blue regions is out of
  the vesicle.}
\end{figure*}

>>>>

%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
%Physics}
\title{Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement}

@@

%
%\paragraph{Literature to maybe cite}
%\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
%happens in regions where proteins congregate and this can lead to
%semi-permeability?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Formulation}
We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:schematics}.
To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$) with an outward normal $\nn$.
On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
and the membrane velocity $\dot{\bf x}$ \cite{yao-mor2017}:
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
is the arclength along the membrane, see figure~\ref{fig:schematics}. Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=1 \mu$m/s. Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution 
($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-3}:10^{-7}$.  Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
In the following we will explore both.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Effects of membrane water permeability}
We consider a single semi-permeable vesicle in familiar configurations to highlight the effects of membrane water permeability.
In free space we put a semi-permeable vesicle in a quiescent flow, a planar shear flow and a Poiseuille flow.
We also consider a semi-permeable vesicle in confinement: a long channel and a contracting channel.
For each example, we fix the vesicle length and examine the enclosed area as a dynamical consequence of water flow, vesicle shape deformation and membrane tension distribution.

In experiments vesicle under shear flows are measured for a minute (chapter 19 in \cite{Dimova2020_GVB}), a duration over which vesicle can be assumed impermeable \cite{AbkarianViallat2005_BJ}. Our simulations of a semi-permeable vesicle
in these flows show that water permeability may lead to different vesicle hydrodynamics over a time scale of 10 to 100 minutes. {\bf YNY: is this correct? The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
For vesicles in a narrow micro-fluidic channel, the typical time scale is of $ms$ \cite{abk-fai-sto2006}. Our simulations show that strong confinement can lead to amplification of water permeability at such short time scale.
%
%all vesicles have a length
%$L$, but the area is not conserved because of semi-permeability. We vary
%the initial vesicle reduced area, the permeability rate, and the flow
%rate. For all simulations, the bending modulus is $10^{-19}J$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}

Our analysis shows that a semi-permeable vesicle in a quiescent flow
relaxes to a circle at a rate that is proportional to $\beta$, and the
steady state tension is $\Lambda = 2\pi^2/L^2$, see Supplementary Material. 
Our analysis further shows that the time for 
a semipermeable vesicle to deviate from its initial reduced area and to reach its
steady state is proportional to $\beta^{-1}$. For this reason, our numerical results below 
are reported in terms of the scaled time $\beta t$.

%This is verified for a
%vesicle with initial reduced area $\nu = 0.65$ and with different
%semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
%the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
%to be within 1.3\% of its steady state reduced area, and the required
%time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
%1.3\% of its initial reduced area. Both times are proportional to
%$\beta^{-1}$, and for this reason, our numerical results are reported in
%terms of the scaled time $\beta t$.
%\begin{table}[htp]
%  \centering
%  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
%  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
%  inflating ($t_\mathrm{inflate}$).}
%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
%    $\beta$ & $t_\mathrm{steady}$  & ratio 
%            & $t_\mathrm{inflate}$ & ratio \\
%    \midrule
%    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
%              & $2.17 \times 10^{-2}$ & --- \\ 
%    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
%                $1.25 \times 10^{-1}$ & 5.76 \\
%    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
%                $1.59 \times 10^{0}$ & 12.72 \\
%    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
%                $2.19 \times 10^{1}$ & 13.77 \\
%    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
%                $2.14 \times 10^{2}$ & 9.77 \\
%    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
%                $2.20 \times 10^{3}$ & 10.14 \\
%    \bottomrule
%  \end{tabular}
%\end{table}

In Figure~\ref{fig:relaxationComposite}, we examine the transient
dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
initial configurations. The vesicles on the left are color-coded by the permeable flux: red denotes a flux into the vesicle, and blue denotes a flux out of the vesicle.
First we observe
that even though the vesicle is inflating to a circle (meaning that
there is a net flux into the vesicle), there are regions where the flux
is out of the vesicle.

For the vesicle with an initial reduced area ($\alpha(0)=0.12$ in the bottom row) we observe that vesicle deflates (blue regions) first due to the high interior capillary pressure.  Over time
all vesicles inflate and as expected, each vesicle eventually
reaches a circular shape with reduced area $\alpha=1$. 
%These regions are denoted in blue and are only present at early times. 
Finally, the vesicles's reduced area do not 
change by much at early times, and intermediate shapes of semi-permeable vesicles
resemble the shape of an impermeable vesicle. This can be explained by
considering the two terms that contribute to the vesicle velocity: (i)
the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the
force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the
permeability velocity is much smaller than the force balance velocity at
early times, and the semi-permeable vesicle dynamics resembles those of
an impermeable vesicle. As the force balance velocity decreases, the
permeability velocity dominates, and the vesicle begins to inflate to a
circle with no vanishing force and velocity. {\bf YNY: We should put a tick on the time when this transition occurs for each of the vesicles}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Planar Shear Flow}
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a). {\bf YNY: should this be two-column wide?}}
\end{figure}

We consider a semi-permeable vesicle in a planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. 
When $\beta=0$ (impermeable case), a vesicle's reduced area
and viscosity contrast determine whether it tank treads or
tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Similar to the
dynamics of an impermeable vesicle, a semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics. Since we
consider semi-permeable vesicles, there is no viscosity contrast and
we do not observe tumbling.

@@

For a variety of semi-permeability rates
and flow rates, a semipermeable vesicle reaches a steady equilibrium as in Figure~\ref{fig:shearComposite}(a).
Since the final shape is independent of the initial
reduce area,  we initialize the vesicle with reduced
area $\nu = 0.65$ for all simulations in Figure~\ref{fig:shearComposite}(b), where we summarize the steady state vesicle shape and its reduced
area. We see that the flow
rate significantly affects the final vesicle shape, but the
semi-permeability rate has a minor effect. Instead, as we saw in the
quiescent analysis, $\beta$ sets a time scale since the time required
for a vesicle to reach its steady state configuration is proportional to
$\beta^{-1}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure*}[htp]
  \ifTikz
  \centering
  \input{figures/parabolicComposite.tikz}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
  a semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. (b) The steady state inclination
  angle for four different flow velocities. The steady state shapes are
  superimposed. (c) The reduced area of the slipper formed with the flow
  rate of 800 $\mu m/s$. (d) The vesicle shape shown with the background
  imposed flow. The channel width is 12.5 times larger than the vesicle
  radius. The corresponding reduced area of each vesicle is indicated by
  the marks in plot (c).}
\end{figure*}

We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The non-linear effects of the Poiseuille flow
on the migration of an impermeable vesicle have been well-studied \cite{kao-bir-mis2009}: At a given value of $U$,
there exists a critical reduced volume above which the equilibrium vesicle shape is symmetric (parachute or bullet shapes) and the vesicle stays at $y=0$.
Below this critical reduced volume the equilibrium vesicle moves off the center and is asymmetric (tank-treading slipper shape).
We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}, see Supplementary Material.

%
%
%We examine the effect of the non-linear Poiseuille flow on the migration of
%semi-permeable vesicle. In this experiment, the vesicle is initialized
%above the center line $y=0$, and it migrates towards the center
%line~\cite{dan-vla-mis2009}. 
%
%For an impermeable vesicle, depending on
%the vesicles reduced area and the flow rate, the equilibrium vesicle shape
%is either an axisymmetric parachute or bullet, or an asymmetric
%tank-treading slipper~\cite{kao-bir-mis2009}. 
%We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}.
%One of the most salient features of an impermeable vesicle in the Poiseuille flow is that, 
%%
%%To validate our methods,
%%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%%for the steady state shape of an impermeable vesicle
%%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%%qualitatively agree, Kaoui et al.~report that the vesicles with
%%$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%%are undergoing a tank treading motion, and we therefore report them as
%%asymmetric slippers.
%
%Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow. 
Using several initial
reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
final vesicle configurations are in
Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
%
As observed for the planar shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the steady state reduced area in
Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U
= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper. We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow. The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
Cells experience stretching and release messengers when they pass through capillary vessels \cite{Wan2008_PNAS,ForsythWan2011_PNAS,Pak2015_PNAS}.
Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for successful passages.
Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a cross section smaller than the cell radius).
Based on the findings in 
%We consider the effect of stenosis on a semi-permeable vesicle. Inspired
%by an experiment that measures the effects of cells on the dynamical
%pressure-drop variations along a micrometer-sized
\cite{abk-fai-sto2006}, we first examining the effect of
semi-permeability on the pressure fluctuation across a stenosed
geometry. In this experiment, a pressure drop is used to squeeze a
red blood cell (RBC) through a constriction with diameter $5\mu$m and
length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow rate is chosen so that
the residency time of the RBC in the constriction agrees with the
experimental results. When the RBC enters the constriction, the result
is an increase in the pressure drop required to maintain a constant flow
rate, and the difference between these pressures is called the excess
pressure. We consider both an impermeable and semi-permeable vesicle
with initial reduced area $\nu = 0.65$ passing through a constricted
geometry and compute the pressure drop between the inlet and outlet of
the constriction. In Figure~\ref{fig:stenosisComposite}(c), we plot the
excess pressures. The impermeable case agrees with experimental
results~\cite{abk-fai-sto2006} (see Figure 3), and the results indicate
that less pressure is required to maintain a constant flow rate when the
vesicle is semi-permeable. Our simulations indicate the
semi-permeability does affect the excess pressure, and the vesicle's
reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a much longer constriction, and we observe that the reduced area
decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).

@@

%
%\begin{figure}[htp]
%%  \ifTikz
%%  \input{figures/stenosisGeom.tikz}
%%  \fi
%  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
%  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
%  passing through a constriction. The geometry and parameters are chosen
%  to replicate the experiments of Abkarian et
%  al.~\cite{abk-fai-sto2006}.}
%\end{figure}
%
%\begin{figure}[htp]
%%  \ifTikz
%%  \input{figures/stenosisPressureFluctuation.tikz}
%%  \fi
%  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
%  \caption{\label{fig:stenosisPressure} The excess pressure across the
%  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
%  denote the start and end of the constriction. The results are
%  qualitative agreement with~\cite{abk-fai-sto2006}.}
%\end{figure}

@@

\begin{figure*}[htp]
  \centering
%  \ifTikz
  \input{figures/contractingComposite.tikz}
%  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, and
  the vesicle height is initially $10\mu$m.}
\end{figure*}
